Measurement and Probability in Fuzzy Quantum Theories

### 2017-02-20 prop_iop.tex
beginning of intro

>>>>

Textbook quantum mechanics asserts that, given a quantum system
described by the wavefunction
$\ket{\psi}=\frac{\sqrt{\pi}}{2}\ket{0}+\frac{\sqrt{4-\pi}}{2}\ket{1}$
and the observable $I$, the probability of observing $\ket{0}$ is
$\frac{\pi}{4}$ and the probability of observing $\ket{1}$ is
$1-\frac{\pi}{4}$. According to the frequency interpretation of
probability, the above assertion implies that when performing a very
large number of experiments on quantum systems described by
wavefunction $\ket{\psi}$, a fraction $\frac{\pi}{4}$ of the
experiments will result in the observation $\ket{0}$ and the remaining
fraction $1-\frac{\pi}{4}$ will result in the observation
$\ket{1}$.

In reality, i.e., in an actual experiment, simulation, or computation,
bounded by space, time, and energy resources, the situation is much
fuzzier: (i) we cannot \emph{exactly} prepare the state $\psi$; (ii)
we cannot \emph{exactly} build a measurement apparatus corresponding
to observable $I$; and (iii) we cannot prepare \emph{exact} replicas
of any state. In other words, we can only perform a limited number of
experiments on quantum systems closely related to wavefunction
$\ket{\psi}$ and using an apparatus that closely approximates
observable $I$. Given any fixed resources, these experiments will
\emph{not} result in the \emph{exact} fraction $\frac{\pi}{4}$ of
observations $\ket{0}$ and $1-\frac{\pi}{4}$ of observations
$\ket{1}$. Indeed, the state of the art algorithms for computing the
$n$th binary digit of~$\pi$ require on the order of
$O\left(n\log^{O\left(1\right)}\left(n\right)\right)$
operations~\cite{journals/moc/BaileyBP97} which means that simply
referring to the $n$th digit of $\pi$ requires more and more resources
as $n$ gets larger.

All of this is well-known. The question is how seriously does it
affect the foundations of quantum mechanics? We believe that the
answer is not evident at all and should be investigated in
detail. Indeed taking such resource bounds into consideration is what
founded computer science as a discipline and has become crucial for
understanding the very nature of computation. Following
Feynman~\cite{Feynman1982Simulating}, Landauer~\cite{Landauer1996188},
and others, one might argue that this resource-bounded perspective is
also crucial for understanding the very nature of physical processes.

\newpage
